\Large \bf Webcam Fuzz Testing: Testing IoT Deployments

### 2015-12-12 Draft Paper/Draft_Paper.tex
final draft

% This version uses the latex2e styles, not the very ancient 2.09 stuff.
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,url}
\begin{document}

@@

A very basic and highly proliferated technology deployed on the internet is an HTTP server. But because of this prevalence, popular servers such as Apache have been thoroughly tested and documented. However, more and more devices are being connected, with an uptake in the Internet of Things (IoT) mentality. 
Fuzz testing is a method of testing in which random, potentially invalid inputs are sent to a program or service in order to test for vulnerabilities. It is often used as either a gray or black-box testing platform for security testing. Fuzz testing can be a very cheap and effective implementation of testing as many inputs can be generated, sent, and analyzed automatically, without the need for a human to monitor. However, a truly random test input could easily not provide anything useful in a reasonable amount of time. Therefore, many solutions (citations needed) propose a different method where random mutation of good inputs is used so that requests that are close to being correct are used.

@@

While these papers looked like they had gathered results from their fuzz testing, they did not release their prototype to the public, and therefore we had to find other publicly available tools that would be able to create fuzz tests. A few of the papers read, such as AspFuzz, mentioned the Peach Fuzzing Platform~\cite{peach} as a tool widely used in this type of testing. We were also able to find widely available tools like AutoFuzz~\cite{autofuzz}, American Fuzzy Lop (AFL)~\cite{afl}, and Pathod/Pathoc~\cite{pathod}. More discussion on these tools is presented in section 3.1.2.

When specifically referring to fuzz testing on IoT devices, we were unable to find much research on this subject. Therefore, we chose this specific field to focus our research.

\section{Experimental Methodology}
In order to create meaningful experiments, the devices under test had to be purchased and evaluated further. Points of attack were gathered, evaluated, and implemented using the available fuzzing tools in order to better attempt to find interesting results.

\subsection{IP Cameras}
The two cameras we purchased were a D-Link Day \& Night Wi-Fi Camera (DCS-934L)~\cite{dlinkCam} and a Pyle Home Indoor Wireless/Wired P2P IP Network Camera (PIPCAM5). The cameras support the following protocols:
\begin{itemize}
	\itemsep-.5em
	\item IPv4, ARP, TCP, UDP, ICMP
	\item DHCP Client
	\item NTP Client (D-Link only)
	\item DNS Client
	\item DDNS Client
	\item SMTP Client
	\item FTP Client
	\item HTTP Server
	\item PPPoE
	\item UPnP port forwarding
	\item RTP, RTSP, RTCP (D-Link only)
	\item LLTD (D-Link only)
	\item GPRS (Pyle only)
\end{itemize}
Though both cameras supported many network protocols, we focused on fuzzing the \textit{alphapd} and \textit{mini-httpd} HTTP servers and the application layers of each of the cameras. We thought the HTTP server protocols and application layers would be the most interesting to fuzz. Most of the other protocols supported were only client protocols, which we felt would be less interesting to fuzz, yet still valuable. We leave testing these other protocols for future work.

@@

\subsubsection{Tools}
Pathoc was used to implement HTTP fuzzing. Pathoc turned out to be fairly simple and straightforward to use, as it was just a command line interface tool that generated HTTP requests such as GET and POST. Because we focused on HTTP, this single protocol application was still very appealing to us. This program allowed us to specify the type of HTTP command, and inject whatever we wanted into the header and body fields while still creating a command with valid syntax. It also has fuzzing capabilities as it is able to inject random bytes anywhere in the request, as well as generate random strings of a desired length and place them in portions of a request. Because of its ease of use and the capability to be used in a simple Bash script, we chose Pathoc v0.14 as our fuzzing platform.

There are a number of different network fuzzers available, including Peach, AutoFuzz, American Fuzzy Lop (AFL). AFL, would be useful as a tool mainly for file testing, where good files as inputs to tools would be mutated and input back into a program for evaluation. This may be a valuable tool for future work in testing the FTP protocols in the cameras.

AutoFuzz has built in support for MSN, SMTP, and FTP protocols, and relied on capturing actual traffic in order to create a state machine. While both of the cameras used in testing supported both SMTP and FTP, they were only clients, and therefore less likely to accept inputs. We attempted to, but were ultimately not able to capture SMTP or FTP traffic from the cameras.

@@

A short example from our script is shown below. We used variables to control the inputs to the pathoc command. For example \textit{\$cmd} might represent an HTTP GET or POST, \textit{\$b1} represents the contents of the HTTP body, and \textit{\$auth} represents the header with authentication credentials. The output is checked, and server responses with \textbf{HTTP/1.1 200} are marked `good' and all others are marked `bad'. 
\begin{verbatim}
for (( i=1; i<=$max; i++ ))
do	
d=$(( ($i*100)/$max ))
r=$(( $RANDOM % 100 + 1 )) #Random [1..100]

@@

It is important to note that if the server doesn't respond with \textbf{HTTP/1.1 200}, it does not necessarily mean that it is bad. This is just the metric we used to try and identify possible interesting responses. Some interesting responses we found are detailed in the Results section. Both cameras were tested with and without authorization credentials, in an effort to identify possible security vulnerabilities.

@@

We also wrote a separate script to scour the log files and aggregate the total number of responses in various categories. We used some of this data for the Pyle camera to generate tables~\ref{tab:Pyle_Good_CGI} and ~\ref{tab:Pyle_Rand_CGI}.

\subsection{Platforms}
Pathoc was run in a Bash script on a virtual Linux machine inside Oracle's VM VirtualBox 5.0.10. Two different Windows 10 laptops were used to run the  Linux Virtual Machines (VMs). One computer ran a 32-bit Ubuntu 12.04 VM with 2.0GiB of dedicated RAM. The other computer was using the All-in-one SDN App Development Starter VM, an image based off of 64-bit Ubuntu 14.04, from SDNHub.org.

@@

\section{Results}
We began our research with this question in mind: \textit{Can we use fuzzing to discover interesting bugs or vulnerabilities in a network-connected device?} At this point in our research, we have not identified any critical bugs in the cameras or inputs that would completely disable the system. We did, however, identify several events or responses that are of interest. We were watching the video output of the cameras during some of the fuzz testing, and we did notice some freezing and lagging of the video feed. We did not record video or attempt to qualify the video output at this stage of our project.

TO weed out the `good' responses from the `bad' responses, the HTTP response codes were examined. There are several categories of HTTP responses: 
\begin{enumerate}
\item HTTP 2xx - successfully received, understood, and accepted.
\item HTTP 3xx - redirection, or further action required to fulfill request.
\item HTTP 4xx - client error, or some sort of bad request
\item HTTP 5xx - server is aware that it has erred or is incapable of fulfilling request.
\end{enumerate}
We decided to categorize all but HTTP 2xx responses as `bad'. We also discovered other interesting events:
\begin{enumerate}
	\item Response timeouts - pathoc was able to issue the HTTP request but the server didn't respond within the specified time frame.
	\item Connection timeouts - pathoc could not establish a TCP connection with the server after attempting for some period of time.
	\item Invalid server response: Server disconnect
	\item (null) - The server responded but left the identifier blank.
\end{enumerate}

As of Dec 4,2015 we have run more than 250,700 fuzzing tests. As of yet, there has not been any input found that would completely disable the cameras. However, some inputs do cause slow downs. Some of the interesting events like connection timeouts may be much more interesting if we could determine that the reason the connection could not be made was that the server had been disabled or was restarting itself. There is future work in further analyzing the data that we have collected. We have the log files that show the inputs that generated these responses. Future work would be to gather and replay these inputs and scrutinize the outputs further.

@@

An interesting result was also the difference in the time taken to run the same command on a Ubuntu VM comapred to the Raspberry Pi. We noticed that although the small computer is very powerful, it had a significant time overhead in our setup. The results of a test consisting of 5000 valid CGI commands to the Pyle camera is shown in table~\ref{tab:VMvsPi}. As we can see, they both generated a similar amount of HTTP responses in the 400 and 500 range, but the Rpi took almost 450\% longer to do it. We suspect it may have to do with the smaller computer having slower I/O speeds for both the USB flash drive and the network interface. All USB ports are also run on one controller, leading to a slowdown if many are used at the same time.

[TODO- refine and analyze this cause more]
We found we could trigger an `HTTP 500 Internal Server Error' with a very long string (70000 byte) in the GET request. The pathoc command looked like 
\begin{verbatim} pathoc -n 1 -t 5 -e -p -q  $ip 
`get:@70000,ascii:b@100,ascii:h$auth '  \end{verbatim}

[TODO- add some distributions for the full 250,000 tests, including non-HTTP coded events]

@@

A major discovery made, unrelated to fuzzing, occurred in the information-gathering stage of the project. Both of the cameras used HTTP Basic or Digest access authentication, which encodes the username:password combinations. Wireshark was able to capture the authentication for logging into the cameras in plain text. This has important ramifications, because all an attacker would need to do would be to use Wireshark or some other network protocol analyzer to capture traffic on the network the camera is on. Once the authentication token is discovered, an attacker could append it to the header of any HTTP message desired, and the camera would accept it as authentic.

\begin{figure}[h b]
\centering
\includegraphics[width=1.9\linewidth]{dist}
\caption{Distribution of 205,000 Response Codes}
\label{fig:dist}
\end{figure}

\section{Future Work}
We have many ideas to improve this project in the future. One obvious improvement would be to fuzz these devices on multiple protocols, not just the HTTP servers. Any one of these other protocols could provide a potential entry point for an attack. The testing framework could also be improved by recognizing interesting outputs, and repeating the inputs that caused them with slight mutations. This might be a more active approach to identifying interesting vulnerabilities and bugs. An HTTP validator could be used to review the responses from the camera servers to verify correct responses and aid in the identification of invalid or buggy responses.

One of the main ideas that we did not have time to implement was to record the video output from each camera during the fuzzing process, and `measure' the quality. We would be interested in video lag, frame drops or freezes, or other events that would make the camera unfit for security applications. The measure of quality is difficult to define, and was beyond the scope of our current project.

%\begin{figure*}
%\centering
%\includegraphics[width=1.9\linewidth]{Pyle_Rand_CGI}
%\caption{5550 fuzz tests on Pyle camera with random commands}
%\label{fig:Pyle_Rand_CGI}
%\end{figure*}

\subsection*{Acknowledgments}
We would like to thank our shepherd, Dr. Eric Eide in providing invaluable insight and assistance with two poor ECE students completing a CS project.

>>>>

% This version uses the latex2e styles, not the very ancient 2.09 stuff.
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,url,wrapfig}
\begin{document}

@@

A very basic and highly proliferated technology deployed on the internet is an HTTP server. Because of this prevalence, popular servers such as Apache have been thoroughly tested and documented. However, more and more devices are being connected, with an uptake in the Internet of Things (IoT) mentality.

Fuzz testing is a method of testing in which random, potentially invalid inputs are sent to a program or service in order to test for vulnerabilities. It is often used as either a gray or black-box testing platform for security testing. Fuzz testing can be a very cheap and effective implementation of testing as many inputs can be generated, sent, and analyzed automatically, without the need for a human to monitor. However, a truly random test input could easily not provide anything useful in a reasonable amount of time. Therefore, many solutions propose a different method where random mutation of good inputs is used so that requests that are close to being correct are used.

@@

While these papers showed promising results from their fuzz testing, they did not release their prototypes to the public, and therefore we had to find other publicly available tools that would be able to create fuzz tests. A few of the papers read, such as AspFuzz, mentioned the Peach Fuzzing Platform~\cite{peach} as a tool widely used in this type of testing. We were also able to find widely available tools like AutoFuzz~\cite{autofuzz}, American Fuzzy Lop (AFL)~\cite{afl}, and Pathod/Pathoc~\cite{pathod}. More discussion on these tools is presented in section 3.1.2.

We were unable to find much research specifically referring to fuzz testing on IoT devices. Therefore, we chose this specific field to focus our research efforts on.

\section{Experimental Methodology}
In order to create meaningful experiments, the cameras under test had to be purchased and evaluated further. We gathered information on the cameras, evaluated points of attack, and implemented fuzzing techniques using available tools in order to better attempt to find interesting results.

\subsection{IP Cameras}
The two cameras we purchased were a D-Link Day \& Night Wi-Fi Camera (DCS-934L)~\cite{dlinkCam} and a Pyle Home Indoor Wireless/Wired P2P IP Network Camera (PIPCAM5). The cameras support the following protocols:
\begin{itemize}
	\itemsep-.5em
	\item IPv4, ARP, TCP, UDP, ICMP
	\item DHCP Client
	\item NTP Client (D-Link only)
	\item DNS Client
	\item DDNS Client
	\item SMTP Client
	\item FTP Client
	\item HTTP Server
	\item PPPoE
	\item UPnP port forwarding
	\item RTP, RTSP, RTCP (D-Link only)
	\item LLTD (D-Link only)
	\item GPRS (Pyle only)
\end{itemize}
Though both cameras supported many network protocols, we focused on fuzzing the \textit{alphapd} and \textit{mini-httpd} HTTP servers and the application layers of each of the cameras. We leave testing these other protocols for future work.

@@

\subsubsection{Tools}
We used Pathoc to implement HTTP fuzzing. Pathoc turned out to be fairly simple and straightforward to use, as it was just a Linux command line interface tool that generated HTTP requests such as GET and POST. Because we focused on HTTP, this single protocol application was very appealing to us. This program allowed us to specify the type of HTTP command, and inject whatever we wanted into the header and body fields while still creating a command with valid syntax. It implements fuzzing by injecting random bytes anywhere in the request, as well as generating random strings of a desired length and placing them in portions of a request. Because of its ease of use and the capability to be used in a simple Bash script, we chose Pathoc v0.14 as our fuzzing platform.

There are a number of different network fuzzers available, including Peach, AutoFuzz, and American Fuzzy Lop (AFL). AFL, would be useful as a tool mainly for file testing, where good files as inputs to tools would be mutated and input back into a program for evaluation. This may be a valuable tool for future work in testing the FTP protocols in the cameras.

AutoFuzz has built in support for MSN, SMTP, and FTP protocols, and relied on capturing actual traffic in order to create a state machine. While the cameras used in testing supported both SMTP and FTP, they were only clients, and therefore less likely to accept inputs. We attempted to, but were ultimately not able to capture SMTP or FTP traffic from the cameras.

@@

A short example from our script is shown below. We used variables to control the inputs to the pathoc command. For example \textit{\$cmd} might represent an HTTP GET or POST, \textit{\$b1} represents the contents of the HTTP body, and \textit{\$auth} represents the header with authentication credentials. The output is checked, and server responses with HTTP/1.1 200 are marked `good' and all others are marked `bad'. 
\begin{verbatim}
for (( i=1; i<=$max; i++ ))
do	
d=$(( ($i*100)/$max ))
r=$(( $RANDOM % 100 + 1 )) #Random [1..100]

@@

It is important to note that if the server doesn't respond with HTTP/1.1 200, it does not necessarily mean that it is bad. This is just the metric we used to try and identify possible interesting responses. Some interesting responses we found are detailed in the Results section. Both cameras were tested with and without authorization credentials, in an effort to identify possible security vulnerabilities.

@@

We also wrote a separate script to scour the log files and aggregate the total number of responses in various categories. We used some of this data for the Pyle camera to generate tables 1 through 3.

\subsection{Platforms}
Two different Windows 10 laptops were used to run Linux Virtual Machines (VMs) using Oracle's VM VirtualBox 5.0.10. One computer ran a 32-bit Ubuntu 12.04 VM with 2.0GiB of dedicated RAM. The other computer was using the All-in-one SDN App Development Starter VM, an image based off of 64-bit Ubuntu 14.04, from SDNHub.org.

@@

\section{Results}
We began our research with this question in mind: \textit{Can we use fuzzing to discover interesting bugs or vulnerabilities in a network-connected device?} At this point in our research, we have not identified any critical bugs in the cameras or inputs that would completely disable the system. We did, however, identify several events or responses that are of interest. We were watching the video output of the cameras during some of the fuzz testing, and we did notice some freezing and lagging of the video feed. We did not record video or attempt to qualify the video output at this stage.

It was necessary to weed out the `good' responses from the `bad' responses, so the HTTP response codes were examined. There are several categories of HTTP responses: 
\begin{enumerate}
\item HTTP 2xx - successfully received, understood, and accepted.
\item HTTP 3xx - redirection, or further action required to fulfill request.
\item HTTP 4xx - client error, or some sort of bad request
\item HTTP 5xx - server is aware that it has erred or is incapable of fulfilling request.
\end{enumerate}
We decided to categorize all but HTTP 2xx responses as `bad'. We were most interested in the HTTP 5xx responses, as these indicated server errors. We also discovered other interesting events:
\begin{enumerate}
	\item Response timeouts - pathoc was able to issue the HTTP request but the server didn't respond within the specified time frame.
	\item Connection timeouts - pathoc could not establish a TCP connection with the server after attempting for some period of time.
	\item Invalid server response: Server disconnect
	\item (null) - The server responded but left the identifier blank.
\end{enumerate}

Throughout the course of ten days, we ran more than 250,700 fuzzing tests. Figure 1 shows a distribution of responses for a significant portion of the tests run. As of yet, there has not been any input found that would completely disable the cameras. However, some inputs do cause slow downs. Some events like connection timeouts may be much more interesting if we could determine the specific reason the connection could not be made. There is future work in further analyzing the data that we have collected. We have the log files that show the inputs that generated these responses. Future work would be to gather and replay these inputs and scrutinize the outputs further.

@@

An interesting result was also the difference in the time taken to run the same command on a Ubuntu VM compared to the Raspberry Pi. We noticed that although the small computer is very powerful, it had a significant time overhead in our setup. The results of a test consisting of 5000 valid CGI commands to the Pyle camera is shown in table~\ref{tab:VMvsPi}. As we can see, they both generated a similar number of HTTP responses in the 4xx and 5xx range, but the Rpi took almost 450\% longer to do it. We suspect it may have to do with the smaller computer having slower I/O speeds for both the USB flash drive and the network interface. All USB ports are also run on one controller, leading to a slowdown if many are used at the same time.

We found we could trigger an `HTTP 500 Internal Server Error' with a very long string (70000 byte) in the GET request. The pathoc command looked like 
\begin{verbatim} pathoc -n 1 -t 5 -e -p -q  $ip 
`get:@70000,ascii:b@100,ascii:h$auth '  \end{verbatim}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=2\linewidth]{dist}
	\caption{Distribution of 204,691 Response Codes}
	\label{fig:dist}
\end{figure}

A major discovery, unrelated to fuzzing, occurred in the information-gathering stage of our research. Both of the cameras used HTTP Basic or Digest access authentication, which encodes the username:password combinations. Wireshark was able to capture the authentication for logging into the cameras in plain text. This has important ramifications, because all an attacker would need to do would be to use Wireshark or some other network protocol analyzer to capture traffic on the network the camera is on. Once the authentication token is discovered, an attacker could append it to the header of any HTTP message desired, and the camera would accept it as authentic. It would be possible to completely disable the camera by assigning it to be on a different unreachable network.

\section{Future Work}
We have many ideas to continue this research in the future. One obvious improvement would be to fuzz these devices on multiple protocols, not just the HTTP servers. Any one of these other protocols could provide a potential entry point for an attack. The testing framework could also be improved by recognizing interesting outputs, and repeating the inputs that caused them with slight mutations. This might be a more active approach to identifying interesting vulnerabilities and bugs. An HTTP validator could be used to review the responses from the camera servers to verify correct responses and aid in the identification of invalid or buggy responses. 
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
One of the main ideas that we did not have time to implement was to record the video output from each camera during the fuzzing process, and `measure' the quality. We would be interested in video lag, frame drops or freezes, or other events that would make the camera unfit for security applications. The measure of quality is difficult to define, and was beyond the scope of this research.

\subsection*{Acknowledgments}
We would like to thank our mentor, Dr. Eric Eide in providing invaluable insight and assistance during the course of this research.
